One Year HPC Certification Forum in Retrospective

### 2019-04-17 paper.tex
Anja's related work piece.

>>>>

The SciNet Certificate Program
\footnote{\url{https://www.scinethpc.ca/scinet-certificate-program/}}
 provides course material for three major Computer Science topics: Scientific Computing, High Performance Computing, and Data Science each with several subcategories.
\footnote{\url{https://support.scinet.utoronto.ca/education/mods/certificate_programs_v2/index_public.php}}

Companies like NVIDIA are offering courses in deep learning\footnote{\url{https://www.nvidia.com/de-de/deep-learning-ai/education/}}.
Also Universities like Kennesaw State University providing Online Course for their students in the areas High Performance Computing and Big Data Analytics
\footnote{\url{https://ccse.kennesaw.edu/cs/programs/cert-hpcc.php}}.
\footnote{\url{https://www.ece.seas.gwu.edu/graduate-certificate-high-performance-computing}}
